%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ao Zeng} % Your name
\address{617-893-4312 \\ zeng1@andrew.cmu.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rEducation}{Carnegie Mellon University, School of Computer Science}{Dec 2018}{Major: Computational Data Science (System Track) GPA:3.83}
    {Pittsburgh, PA}
\end{rEducation}
\begin{rEducation}{University of North Carolina at Chapel Hill}{May 2017}{Dual Major: Computer Science and Mathematics \ \ \ \  GPA: 3.81}
    {Chapel Hill, NC}
\end{rEducation}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Course Project}

\begin{rSubsection}{Cloud Computing with Spark}{Spring 2018}{Carnegie Mellon University}{Pittsburgh, PA}{}
    \item Performed ETL, developed and implemented a scalable distributed iterative machine learning program using Apache Spark on AWS.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Distributed System Consensus Protocol and Load Balancing}{Fall 2017}{Carnegie Mellon University}{Pittsburgh, PA}{}
\item Implemented a status replication service for log replication among multiple servers using the Master-Slave model
 in Golang based on the Raft algorithm paper.
\item Built a simple key value store service in Golang using consistent hash and cache for load balancing.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Disk-Oriented Database Storage System}{Fall 2017}{Carnegie Mellon University}{Pittsburgh, PA}
{Implemented fundamental components of a single node, disk-oriented database storage manager in C++, including:}
\item Memory buffer pool using LRU replacement policy for fetching database pages.
\item Lock Manager supporting two-phase locking and strict two-phase locking for concurrency control.
\item Database index using concurrent B+ Tree data structure.
\item Part of the ARIES protocol for database logging and recovery.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Web Application}{Fall 2016}{University of North Carolina}{Chapel Hill, NC}{}
\item Built a prototype web application, allowing user to send real-time messages, share interesting events on
 their calendars, and use third party API to check friends' recent gaming histories.
\item Wrote front end in Javascript using JQuery and AJAX to dynamically generate page contents and adjust display.
\item Designed and implemented back end ORM layer using PHP and SQL.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Experience}
\begin{rResearch}{Splice Machine Inc}{May 2018 - Aug 2018}
    {Software Developer}{}{}
    \item Experienced a full development cycle, where I designed and implemented the support for Python stored procedure and user-defined function to the database from scratch by modifying the
    SQL parser, the query plan and the code generation modules.
    \item Presented multiple times to the entire development team, resulting in positive feedback and helpful advice.
\end{rResearch}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages:&C/C++, Java, Golang, Python, SQL, JavaScript, PHP\\
Application Program:&Mathematica, \LaTeX\\
Frameworks and Tools: &jQuery, SciPy, Git, Matplotlib
\end{tabular}

\end{rSection}

\begin{rSection}{Awards}
    Dean's List ($\times$4), University of North Carolina at Chapel Hill 
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
